R Notebook

### 2019-01-30 microbiome_online_MRD_working.Rmd
updated

```{r}
	setwd("/omega/bashscripts")

@@

library(hrbrthemes)
library(gcookbook)
library(tidyverse)

library(phyloseq)
library(microbiome)
library(knitr)
library(ggpubr)

>>>>

```{r}
	setwd("/Users/rezahaji-dehabadi/scripts/workspace")

@@

library(hrbrthemes)
library(gcookbook)
library(tidyverse)
library(gdtools)
library(phyloseq)
library(microbiome)
library(knitr)
library(ggpubr)
